Notebook with AMP-AD RNA-seq network analysis results

### 2020-09-22 manuscript.Rmd
updates

```{r}
dummyDf <- targetedEnrichment$ad
dummyDf$fisherOR[dummyDf$adj.pval>=0.05] <- NA
dummyDf <- dplyr::left_join(dummyDf,modMeta)
#dummyDf$ModuleBrainRegion <- factor(dummyDf$ModuleBrainRegion,levels = unique(dummyDf$ModuleBrainRegion))
dummyDf <- dplyr::filter(dummyDf,category!='Nominated_targets' & category!='Mayo_simple' & category != 'omim' & category != 'jensenDisease' & category != 'wikipathwaysMouse' & category != 'pantherAmyloid')

dummyDf$category <- gsub('Mayo_comprehensive',
                         'Mayo Oligo Modules',
                         dummyDf$category)

dummyDf$category <- gsub('Columbia_Broad_Rush_m109',
                         'ROSMAP m109',
                         dummyDf$category)

@@

@@

dummyDf$category <- factor(dummyDf$category,
                           levels = rev(c('genecards',
                                       'pantherPresenilin',
                                       'dbgap',
                                       'igap',
                                       'omimExpanded',
                                       'biocarta',
                                       'wikipathwaysHuman',
                                       'kegg',                                       
                                       'MSSM',
                                       'Mayo_RNAseq',
                                       'Emory',
                                       'Columbia_Broad_Rush_m109')))

@@

g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='AD Signature',
                 outputFile = TRUE,
                 fileName = '~/Desktop/updatedFiguresFeb52020/figure1d.tiff',
                 scaleValue = 2)
```

>>>>

```{r}
dummyDf <- targetedEnrichment$ad
dummyDf$fisherOR[dummyDf$adj.pval>=0.05] <- NA
dummyDf <- dplyr::left_join(dummyDf,modMeta)
#dummyDf$ModuleBrainRegion <- factor(dummyDf$ModuleBrainRegion,levels = unique(dummyDf$ModuleBrainRegion))

dummyDf <- dplyr::filter(dummyDf,category!='Nominated_targets' & category!='Mayo_simple' & category != 'omim' & category != 'jensenDisease' & category != 'wikipathwaysMouse' & category != 'pantherAmyloid')

dummyDf$category <- gsub('Mayo\\_comprehensive',
                         'Mayo Oligo Modules',
                         dummyDf$category)

dummyDf$category <- gsub('Columbia\\_Broad\\_Rush\\_m109',
                         'ROSMAP m109',
                         dummyDf$category)

@@

dummyDf$category <- gsub('igap',
                         'IGAP',
                         dummyDf$category)

dummyDf$category <- gsub('biocarta',
                         'Biocarta',
                         dummyDf$category)

dummyDf$category <- gsub('genecards',
                         'Genecards',
                         dummyDf$category)

dummyDf$category <- gsub('kegg',
                         'KEGG',
                         dummyDf$category)

dummyDf$category <- gsub('wikipathwaysHuman',
                         'Wikipathways Human',
                         dummyDf$category)

dummyDf$category <- gsub('pantherPresenilin',
                         'Panther Presenilin',
                         dummyDf$category)

dummyDf$category <- gsub('dbgap',
                         'dbGaP',
                         dummyDf$category)

dummyDf$category <- gsub('omimExpanded',
                         'OMIM Expanded',
                         dummyDf$category)

@@

dummyDf$category <- factor(dummyDf$category,
                           levels = rev(c('Genecards',
                                       'Panther Presenilin',
                                       'dbGaP',
                                       'IGAP',
                                       'OMIM Expanded',
                                       'Biocarta',
                                       'Wikipathways Human',
                                       'KEGG',                                       
                                       'MSSM Oligo Modules',
                                       'Mayo Oligo Modules',
                                       'Emory AD Modules',
                                       'ROSMAP m109')))

@@

g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='AD Gene Set',
                 outputFile = TRUE,
                 fileName = '~/Desktop/updatedFiguresFeb52020/figure1d.tiff',
                 scaleValue = 2)
```
